---
title: "usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package provides an example dataset (5000 observations). Suppose we are interested in the relationship between `y` and `x`. `x` is not in this dataset, because it is perhaps expensive to collect. Instead, we have another variable `w`, which is from an automated classifier trained to predict `x`.

```{r researchdata}
library(misclassificationmodels)
head(research_data)
```

The automated classifier misclassifies `x`. In order to find out the extent of misclassification, we produced another validation dataset `val_data` (300 observations).

```{r valdata}
head(val_data)
```

The variable `w` is a **proxy**, whereas `x` is the **ground truth** of the proxy. The confusion matrix:

```{r confusion}
table(proxy = val_data$x, groundtruth = val_data$w)
```

The naive estimator is based on the analysis of using the proxy as if it were the ground truth:

```{r naive}
library(MASS)
glm(y ~ w + z, data = research_data)
```

The feasible estimator is based on the analysis of only the validation dataset, which is quite different from the naive estimator.

```{r feasible}
glm(y ~ x + z, data = val_data)
```

## Maximum Likelihood Adjustment

Maximum Likelihood Adjustment (MLA) is based on the general likelihood modeling framework drawn from Carroll et al. (2006). The function is very similar to glm() but with two changes:

* The formula interface has been extended with the double-pipe operator to denote proxy variable. For example, `x || w` indicates `w` is the proxy of the ground truth `x`.
* The validation data (with both proxy and ground truth, as well as another variables, e.g. `y` and `z`) must be provided as `data2`

```{r mla}
res <- glm_fixit(formula = y ~ x || w + z, data = research_data, data2 = val_data)
res
```

Using the `summary` method to get a comparison between the three estimators: naive, feasible, and MLA. The naive estimator is biased.

```{r mla_output}
summary(res)
```

## Outcome families

Currently the method support two families of output: Gaussian (default) and binomial (a.k.a. logistic regression).

```{r mla_logistic1}
research_data_binary <- research_data
median_y <- median(research_data_binary$y)
research_data_binary$y <- research_data_binary$y > median_y

val_data_binary <- val_data
val_data_binary$y <- val_data_binary$y > median_y

head(research_data_binary)
```

```{r mla_logistic2}
res2 <- glm_fixit(formula = y ~ x || w + z, data = research_data_binary, data2 = val_data_binary, family = binomial("logit"))
summary(res2)
```

## Dependent variable

The same method can also be applied to regression analysis where the dependent variable is a proxy.

```{r researchdata2}
head(research_data2)
```

```{r fixit2}
res3 <- glm_fixit(formula = y || w ~ x + z, data = research_data2,
                  data2 = val_data2, family = binomial("logit"))
summary(res3)
```
